---
title: "Assignment 9 Exercise 2"
author: "Radhakrishnan Ponisseril"
date: "8/7/2021"
output: pdf_document
---

```{r include=TRUE, echo=FALSE}
library(ggm)
library(ggplot2)
library(readr)
library(pastecs)
library(readxl)
library(plyr)
library(dplyr)
library(magrittr)
library(purrr)
library(stringr)
library(QuantPsyc)
library(caTools)
library(survival)
```

## Fit a Logistic Regression Model to binary-classifier-data.csv dataset

The dataset (found in binary-classifier-data.csv) contains three variables; label, x, and y. The label variable is either 0 or 1 and is the output we want to predict using the x and y variables.
  1.  What is the accuracy of the logistic regression classifier?
  2.  Keep this assignment handy, as you will be comparing your results from this week to next week.
  
```{r include=TRUE, echo=FALSE, message = FALSE, warning = FALSE}
setwd("/Users/RajeevP/dsc520")
binaryClassifier_df <- read.csv("data/binary-classifier-data.csv", stringsAsFactors = FALSE)
binaryClassifierModel <- glm(label ~ x + y, data = binaryClassifier_df, family = binomial())
summary(binaryClassifierModel)
```
```{r include=TRUE, , echo=FALSE}
res <- predict(binaryClassifierModel, binaryClassifier_df, type = "response")

# Confusion Matrix
confMatrix <- table(Actual_value = binaryClassifier_df$label, Predicted_value= res>0.5)
confMatrix

# Accuracy of Model
accuracy <- (confMatrix[[1,1]] + confMatrix[[2,2]]) / sum(confMatrix) * 100
print(paste("Accuracy of the model: ",round(accuracy,digits = 2) , "%"))
```