---
title: "Final Project Step 2"
author: "Radhakrishnan Ponisseril"
date: "8/8/2021"
output: pdf_document
---

```{r include=TRUE, echo=FALSE, message = FALSE, warning = FALSE}
library(ggm)
library(ggplot2)
library(readr)
library(magrittr)
library(purrr)
library(pastecs)
library(readxl)
library(plyr)
library(dplyr)
library(stringr)
library(QuantPsyc)
library(caTools)
library(survival)
```

## How to import and clean my data

I have used read_csv() to import the data into a data frame and removed duplicates
Fields that are retained from the original data set that can be utilized to predict the loan status

id	
member_id	
loan_amnt	
funded_amnt	
funded_amnt_inv	
term	
int_rate	
installment	
home_ownership	
annual_inc	
verification_status	
issue_d	
loan_status	
addr_state	
fico_range_low	
fico_range_high

## What does the final data set look like?
```{r include=TRUE,echo=FALSE, message = FALSE, warning = FALSE}
setwd("/Users/RajeevP/dsc520")
lendClubLoans_df <- read_csv("data/lending_club_loans.csv")
head(lendClubLoans_df)
```
## What information is not self-evident?
None

## What are different ways you could look at this data?
1. Interest Rate Vs Loan Status (Charged off or not)
2. Annual Income Vs Loan Status (Charged off or not)

## How do you plan to slice and dice the data?
There are multiple status of loans in the loan status field. I am going to take customers those are charged off into one variable and others into another variable of data frame type.

## How could you summarize your data to answer key questions?
I will use summary() function on the model in providing the R and R-squared if Linear model and AIC. I will use Deviations if it is a Logistic regression. It will provide us the information on how predictors influence the outcome

## What types of plots and tables will help you to illustrate the findings to your questions?
Scatter plots, line graphs, histograms

## Do you plan on incorporating any machine learning techniques to answer your research questions? Explain.
I will use logistic Regression on the data as Charge off Yes or No is the outcome based on the predictors.
